%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{tabularx}
\usepackage{nth}
\usepackage{enumitem}
\setlist{nolistsep}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Jackie(Junrui)}{Yang}{ \urlstyle{same}\url{http://www.yangjunrui.com} \\
\href{mailto:jackieyang51@gmail.com}{jackieyang51@gmail.com} | +86-136-9153-0067
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Beijing No.8 Middle School}
\descript{Gifted and Talented Class}
\location{2006.09-2009.06}
\sectionsep

\sectionsep

\subsection{High School affiliated to Renmin University}
\location{2009.09-2012.06}
\sectionsep

\subsection{Peking University}
\descript{BS in Computer Science}
\location{2012.09-2016.06 (Expected)}
GPA:
\begin{description}
\item[\nth{1} semester] 3.46
\item[\nth{2} semester] 2.98
\item[\nth{3} semester] 3.43
\item[\nth{4} semester] 3.66
\end{description}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Links} 
% Github:// \href{https://github.com/deedydas}{\custombold{deedydas}} \\
% LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\custombold{debarghyadas}} \\
% YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\custombold{DeedyDash007}} \\
% Twitter://  \href{https://twitter.com/debarghya_das}{\custombold{@debarghya\_das}} \\
% Quora://  \href{https://www.quora.com/Debarghya-Das}{\custombold{Debarghya-Das}}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Advanced Machine Learning \\
% Open Source Software Engineering \\
% Advanced Interactive Graphics \\
% Compilers + Practicum \\
% Cloud Computing \\
% \sectionsep

% \subsection{Undergraduate}
% Information Retrieval \\
% Operating Systems \\
% Artificial Intelligence + Practicum \\
% Functional Programming \\
% Computer Graphics + Practicum \\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
% Unix Tools and Scripting \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{English}
TOFEL: 107
\subsection{Programming}
C/C++ \textbullet{} Python \textbullet{} Javascript  \textbullet{} Scheme  \textbullet{} .Net and C\# \textbullet{} Swift and Objective-C on OS X/iOS
\subsection{Others}
Experienced in micro controller programming (ATMega and Cortex-M platform)
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
% \begin{tabular}{rll}
% 2011 &National Olympiad in Informatics in Provinces, Second Prize\\
% 2012 &Peking University ACM/ICPC, Third Prize\\
% 2013 &International Youth Innovation Competition, Golden Prize\\
% 2013 &Peking University Industrial Engineering Competition, First Prize\\
% 2013 &"Challenge Cup" National College Student Curricular Academic Science and Technology Works Competition, Second Prize in Peking University\\
% 2013 &Peking University Prize for social/community work\\
% 2013 &Honorable Mention in Mathematical Contest in Modelling\\
% 2013 &Peking University ACM/ICPC, Third Prize\\
% \end{tabular}
% \sectionsep

\begin{description}
\itemsep0em 
	\item[2011] National Olympiad in Informatics in Provinces, Second Prize\\
	\item[2012] Peking University ACM/ICPC, Third Prize\\
	\item[2013] International Youth Innovation Competition, Golden Prize\\
	\item[2013] Peking University Industrial Engineering Competition, First Prize\\
	\item[2013] "Challenge Cup" National College Student Curricular Academic Science and Technology Works Competition, Second Prize in Peking University\\
	\item[2013] Peking University Prize for social/community work\\
	\item[2013] Honorable Mention in Mathematical Contest in Modelling\\
	\item[2013] Peking University ACM/ICPC, Third Prize\\
	\item[2014] Peking University Founder Prize
	\item[2014] Peking University Innovation Prize
\end{description}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.62\textwidth} 

\section{Profile}
At age 10 I was admitted to the Gifted and Talented class in Beijing No.8 Middle School, and enrolled in Peking University at age 16. Now, I pride myself on my ability in interdisciplinary research and in organizing development projects. My “Pocket Printer” project, in particular, has won many awards. I also take part in many software hardware co-design projects. I have done research at both computer science and bio-engineering labs, giving me insight on automation and cutting edge research in life science.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Huang Lab}
\descript{| Intern, Biodynamic Optical Imaging Center}
\location{2013.6-present |  Peking University }
Build “Cell Picker”, a Computer assisted high throughput single cell acquiring system\\
Built the whole software system and part of the hardware structure.\\
Introduced our project to Chairman Xi when he visited Peking University.\\
Build a bioinformatics program to analyse DNA Barcoding sequencing result.\\
Implement the program.\\
Build a automated droplet generating system\\
Build all the software and hardware system.\\

\runsubsection{Center for Energy-Effecient Computing and Applications}
\descript{| Intern, Reconfigurable Architecture for Wireless Team}
\location{2014.2-present | Intern, Reconfigurable Architecture for Wireless Team, Peking University}
Help build the linux driver for our software defined radio system
Port this system to a more commonly used driver ath9k.

\runsubsection{Microsoft Research Asia}
\descript{| Research Intern, Wireless and Networking research group}
\location{2015.2-present | Beijing}
Under Jacky Shen's guidance, wrote the algorithm part of an indoor location application. Recently I started to work on an innovative research project.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Pocket Printer}
\descript{}
\location{2013.09-2014.09}
Pocket printer is a printer that can fit in a pocket. To achieve this, I cancelled the paper feeding system in traditional printers, and placed a navigating system formed by several mouse navigating sensors. I expected the printer can print the pattern depending on the relative location of the printer. Hardware and software co-design. Lead the development group. Designed the circuit board, the software logic inside the microcontroller, and the client software in phone.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Social}
\runsubsection{Peking University Makerspace}
\descript{Peking University}
\location{2014.11-Now}
Co-founded the Peking University Makerspace as the President of the association. The Peking University Makerspace is an official Peking University student organization. We provide our peers a laboratory to conduct their innovative projects like mine. We also design a series of classes and lectures to teach students basic hardware and software engineering skills along with experience in start-up companies.


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     SOCIETIES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies} 

% \begin{tabular}{rll}
% 2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
% 2014   & National   & The Global Leadership and Education Forum (tGELF)\\
% 2012   &  National  & Golden Key International Honor Society\\
% 2012   &  National   & National Society of Collegiate Scholars\\
% \end{tabular}
% \sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
